% Results
% The progression of the memory usage throughout the job can be shown by plotting the proportional set size (Figure \ref{fig: mc-prmon-pss} and Figure \ref{fig: data-prmon-pss}), resident set size (Figure \ref{fig: mc-prmon-rss} and Figure \ref{fig: data-prmon-rss}), and the virtual memory versus the wall time (Figure \ref{fig: mc-prmon-vmem} and Figure \ref{fig: data-prmon-vmem}.) 

% % Graphs: Bad News
% In Figure \ref{fig: mc-prmon-pss}, Athena \textit{default} uses less memory than any of the basket buffer limit configurations.
% There increased memory usage is about $12.7\%$ in MC proportional set size or as little as  $2.8\%$ for Data as seen in Figure \ref{fig: data-prmon-pss}, see Appendix A. 
% A similar trend persists for the other figures, where MC jobs are taking the greatest hit in memory usage for Figure \ref{fig: mc-prmon-rss} and Figure \ref{fig: mc-prmon-vmem}, when compared to the data derivation jobs in Figure \ref{fig: data-prmon-rss} and Figure \ref{fig: data-prmon-vmem}. 

\subsection{Athena v22.0.16 testing}
The results of this run of testing was done on a nightly build of Athena that is based on version 22.0.16 and looked at both the presence of an upper limit to the basket size (a ``basket-cap") and the presence of a minimum number of entries per branch, the default setting is 10 entries.
PHYSLITE MC derivation production, from Table \ref{Tab: night-mc-outputfs}, sees a 9.9\% increase in output file size when compared to the $\textit{default}$ Athena configuration, and since this configuration only differs by the elimination of the ``min-number-entries" we assume the minimum number of entries per branch should be kept at 10 and left alone.
Table \ref{Tab: night-mc-outputfs} also shows the potential for PHYSLITE MC DAOD output file size reduction by elminiating our ``basket-cap'' (basket buffer limit) altogether.
\input{content/tables/nightly-tables.tex}

\subsection{Athena v24.0.16 testing}
Switching from the nightly build to the stable Athena version 24.0.16, pre-existing derivation jobs were ran for Data and MC to compare between configurations of differing basket size limits.
The results for this set of testing are found from Table \ref{Tab: 24.0.16-data-outputfs} through Table \ref{Tab: 24.0.16-MC-PHYSLITE-no-lim-top-compfs}. 
The following tables are the DAOD output-file sizes of the various Athena configurations for PHYS/PHYSLITE over their respective Data/MC AOD input files.

\input{content/tables/data-fs-tables}

% -------------------------------------------------------------------------------------------------------------------------------

\input{content/tables/mc-fs-tables}

% -------------------------------------------------------------------------------------------------------------------------------


\subsection{Highly compressible branches}
% =====================
% ====== TOP TEN ======
% =====================

Derivation production will produce branches that are initially very large and occupy memory and compress that down to a smaller size.
One thing that we tend to want to avoid is having too much repetition resulting in high compression factors.
If we have many highly compressible branches, more memory will be used, specifically within I/O buffers.
The following tables are an investigation into the highly compressible branches (e.g., the branches with compression factor over $\mathcal{O}(1)$) and might possibly lead to some insight on the increase in memory among the decrease in disk space.

% The tables start with Data PHYS, then move to Data PHYSLITE, then MC PHYS, and lastly MC PHYSLITE. For each, shown are the $\textit{default}$ Athena configuration and the $\textit{no-lim}$ configuration. 
% % ======= DATA PHYS =======
% \input{content/tables/top-ten/data/data-phys-CF.tex}
% \input{content/tables/top-ten/data/data-phys-total.tex}
% \input{content/tables/top-ten/data/data-phys-compressed.tex}
% % ======= DATA PHYSLITE =======
% \input{content/tables/top-ten/data/data-physlite-CF.tex}
% \input{content/tables/top-ten/data/data-physlite-total.tex}
% \input{content/tables/top-ten/data/data-physlite-compressed.tex}
% % ======= MC PHYS =======
% \input{content/tables/top-ten/mc/mc-phys-CF.tex}
% \input{content/tables/top-ten/mc/mc-phys-total.tex}
% \input{content/tables/top-ten/mc/mc-phys-compressed.tex}
% ====== MC PHYSLITE =======

\input{content/tables/top-ten/mc/mc-physlite-CF.tex}
\input{content/tables/top-ten/mc/mc-physlite-total.tex}
\input{content/tables/top-ten/mc/mc-physlite-compressed.tex}


An immediate observation: with the omission of the basket limit, the compression factor increases--this is inline with the original expectation that increased buffer size limits correlate to better compression. 
$\textit{PrimaryVerticesAuxDyn.trackParticleLinks}$ is a branch that consistently has the highest memory usage to disk-space usage ratio of any branch.
I/O buffers are concerned with the total file size of each branch, as it is the uncompressed size of each branch that is held in memory. 
$\textit{HLTNav\_Summary\_DAODSlimmedAuxDyn.linkColNames}$ and others show similar behavior and are consistent with the other DAOD jobs across data, MC, PHYS, and PHYSLITE (the tables of which were omitted for sake of brevity).
Future work could investigate these branches for further optimization.